\GVN{}-Hoist: Hoisting Computations from Branches

### 2016-11-03 slides/gvn-hoist.tex
simplify
remove llvm ir example: it is not really needed

\begin{frame}[fragile]{CFGSimplify limits}
  \begin{columns}[T,onlytextwidth] % align columns
    \column{.4\textwidth}
    \begin{block}{\small Original program}
      \begin{lstlisting}
inv = 1/d;
if (inv >= 0) {
  ta = a * inv;
  tb = b * inv;
} else {
  ta = b * inv;
  tb = a * inv;
}
      \end{lstlisting}
    \end{block}
    \pause
    \column{.1\textwidth}
    \begin{center}
      \vspace{2cm}
      $\longrightarrow$
    \end{center}
    \column{.4\textwidth}
    \begin{block}{\small Expressions hoisted}
      \begin{lstlisting}
inv = 1/d;
x = a * inv;
y = b * inv;
if (inv >= 0) {
  ta = x;
  tb = y;
} else {
  ta = y;
  tb = x;
}
      \end{lstlisting}
    \end{block}
  \end{columns}
\end{frame}

@@

\newlength\someheight
\setlength\someheight{4cm}

\begin{frame}[fragile]{Example}
\begin{adjustbox}{width=\textwidth,height=\someheight,keepaspectratio}
\begin{lstlisting}
define float @f(float %d, float %min, float %max, float %a) {
entry:
  %div = fdiv float 1.000000e+00, %d
  %cmp = fcmp oge float %div, 0.000000e+00
  br i1 %cmp, label %if.then, label %if.else

if.then:                                          ; preds = %entry
  %sub = fsub float %min, %a
  %mul = fmul float %sub, %div
  %sub1 = fsub float %max, %a
  %mul2 = fmul float %sub1, %div
  br label %if.end

if.else:                                          ; preds = %entry
  %sub3 = fsub float %max, %a
  %mul4 = fmul float %sub3, %div
  %sub5 = fsub float %min, %a
  %mul6 = fmul float %sub5, %div
  br label %if.end

if.end:                                           ; preds = %if.else, %if.then
  %tmax.0 = phi float [ %mul2, %if.then ], [ %mul6, %if.else ]
  %tmin.0 = phi float [ %mul, %if.then ], [ %mul4, %if.else ]
  %add = fadd float %tmax.0, %tmin.0
  ret float %add
}
\end{lstlisting}
\end{adjustbox}
\end{frame}

\begin{frame}[fragile]{Example}
\begin{adjustbox}{width=\textwidth,height=\someheight,keepaspectratio}
\begin{lstlisting}
define float @f(float %d, float %min, float %max, float %a) {
entry:
  %div = fdiv float 1.000000e+00, %d
  %cmp = fcmp oge float %div, 0.000000e+00
  %sub1 = fsub float %max, %a
  %sub = fsub float %min, %a
  %mul2 = fmul float %sub1, %div
  %mul = fmul float %sub, %div
  br i1 %cmp, label %if.then, label %if.else

if.then:                                          ; preds = %entry
  br label %if.end

if.else:                                          ; preds = %entry
  br label %if.end

if.end:                                           ; preds = %if.else, %if.then
  %tmax.0 = phi float [ %mul2, %if.then ], [ %mul, %if.else ]
  %tmin.0 = phi float [ %mul, %if.then ], [ %mul2, %if.else ]
  %add = fadd float %tmax.0, %tmin.0
  ret float %add
}
\end{lstlisting}
\end{adjustbox}
\end{frame}

>>>>

\begin{frame}[fragile]{CFGSimplify limits}
  \begin{columns}[T,onlytextwidth] % align columns
    \column{.4\textwidth}
    \begin{block}{\small Original program}
      \begin{lstlisting}
i = 1/d;
if (i >= 0) {
  u = a * i;
  v = b * i;
} else {
  u = b * i;
  v = a * i;
}
      \end{lstlisting}
    \end{block}
    \pause
    \column{.1\textwidth}
    \begin{center}
      \vspace{2cm}
      $\longrightarrow$
    \end{center}
    \column{.4\textwidth}
    \begin{block}{\small Expressions hoisted}
      \begin{lstlisting}
i = 1/d;
x = a * i;
y = b * i;
if (i >= 0) {
  u = x;
  v = y;
} else {
  u = y;
  v = x;
}
      \end{lstlisting}
    \end{block}
  \end{columns}
\end{frame}

@@
